\documentclass[12pt]{article}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage{lipsum}
\usepackage{verse}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{crimson}
\usepackage{tabto}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{bold-extra}

%% The font package uses mweights.sty which has som issues with the
%% \normalfont command. The following two lines fixes this issue.
%\let\oldnormalfont\normalfont
%\def\normalfont{\oldnormalfont\mdseries

%\normalsize

\renewcommand{\baselinestretch}{0.85}
\renewcommand*\rmdefault{lmr}
\setlength{\columnsep}{0cm}
\pagenumbering{gobble}
\renewcommand{\poemtitlefont}{\large\scshape\centering}
%\newcommand{\footnotefont}{\small\scshape\centering}
\renewcommand\Large{\@setfontsize\Large\@xiipt{18}}
\newcommand{\attrib}[1]{% 
  \nopagebreak{\scshape\centering\footnotesize #1\par}
}
\begin{document}

{\fontfamily{lmr}\selectfont\poemtitle{Margin Control}}

%{\fontfamily{lmr}\selectfont{\small\scshape\centering{Chris Romano}}}
\vspace{-0.5em}

\attrib{chris romano} 
\begin{multicols}{2}\settowidth{\versewidth}{\footnotesize 
%\bfseries
 It was nothing like the way I wro}


 \begin{verse}[\versewidth]
            
I lived on county line, \\
my best friend at city limit. \\
We walked to see each other, \\
just 3 miles in between. \\!

Her street a flowing mess \\
of those tireless machines; \\
mine a quiet corridor \\
with twice as many laws, \\
and half the daily download, \\
if even that at all. \\!

Bookish as I was, I thought \\
I'd drawn the longer straw. \\
Surely the ennui would soon \\ 
draw brilliance from my hand. \\!

The torture of the calm \\
cuts bone-deep, or so I’ve heard. \\
The purchase of the artistry \\
of metered spoken word. \\!

But though my mind abuzz, \\
and my will a flaming torch, \\ 
I couldn’t spill the inkwell, \\
all those hours on the porch. \\!

And she, despite her home, \\
and despite that awful noise, \\
found her mind a placid pond, \\
and began to write some poems. \\!

“I need your expert eye,” \\
she told me of her first, \\
to charm me with respect \\
for this craft I’ve so endured. \\!

At first I found it cute, \\
but as I read on more, \\
its beauty beat me down, \\
‘til my heart was on the floor. \\!

It was nothing like the way I wrote, \\
but everything I wanted. \\
I loved her yet I hated \\
that her stupid name was on it. \\!

I told her “pretty good!” \\
Then went home to hide my tears. \\
She must have found those words \\
in that metal noise she hears. \\!

I curse my house for being \\
on the only type of border \\
that does nothing for an artist \\
like the one I must become. \\!

I’ve tried it every way: \\
pen, keyboard, and recorder, \\
yet I’ve had no stroke of genius, \\
and I’m now no longer young. \\!

I curse my dad and mother \\
for the coward’s way they took. \\
My birth in their suburbia; \\
the death of my great book. \\!

I curse the county line, \\
the most useless waste of ink; \\
it's the nullest of partitions, \\
you would miss it if you blinked. \\!

No team would wear its jersey, \\
no army think to storm it. \\
No passersby excited, \\
and not once a single tourist. \\!

In fact, the only people \\
that it matters to are me, \\
the traffic cops and linemen, \\
who would never come for free. \\

— — — — — — — — — — \\
\: 					 \\!
\: 					 \\
\: 					 \\!
— — — — — — — — — — \\

I saw again my best friend, \\
decades we'd now lost. \\
I wondered how it was for her, \\
that gift she'd come across. \\!

My whole life I'd imagined her \\
with pen, so I'd not penned her. \\
I asked about that poem of hers, \\
but she did not remember. \\!

My eyes grew wide and I \\
recited every single line, \\
She said "oh yeah!" \\
but in her eyes \\ 
I saw that she had lied. \\!

I tried to smile back, but \\
could only wear a smirk, \\
running from the topic, \\
I ask what she does for work. \\!

And there I was, a teacher, \\
felt a failure all my life. \\
There she was, a teacher, \\
as if basking in the light. \\!

\end{verse}
\end{multicols}
\end{document}